---
title: "didu-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{didu-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Didu is an R package with four simple functions. The functions are: <br>
- `convert_date_columns` <br>
- `plotting` <br>
- `read_csv_tibble` <br>
- `save_rds_csv` <br>

The package also consists of 3 datasets named `data_dengue.csv`, `tidy_dengue.csv` and `dengue_flu.csv`. These datasets will help with a quick start and introduction to the functions in the didu package. 

## Installation

You can install the development version of didu from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Dian2608/didu")
```

## Loading the library

```
library(didu)
```

## read_csv_tibble
With the `read_csv_tibble` function it is possible to read a .csv file from your folder into R. The function also makes a tibble of the data. In the code chunk below the usage of the function is demonstrated. 

```{r function 1, warning=FALSE, message=FALSE}

data_dengue <- read_csv_tibble("./data/data_dengue.csv")

```

## convert_date_columns
With the `convert_date_columns` function it is possible to convert columns with the yy/mm/dd format to three separate columns. These three columns will be named "year", "month" and "day". The function also changes the data class of the three new columns to numeric. In the chunk below, the function is demonstrated with the dengue_data that comes with the `didu` package. 

```{r function 2, warning=FALSE, message=FALSE}

dengue <- convert_date_columns(data_dengue, date_column = Date)

```

## plotting
The `plotting` function is able to plot data with a matching group variable. It is also possible to determine the title of the plot. In the code chunk below the usage of this function is demonstrated.
```{r function 3, warning=FALSE, message=FALSE}
# Use the read_csv_tibble function to load csv file
dengue_flu <- data_dengue <- read_csv_tibble("./data/dengue_flu.csv")

# Plotting
plotting(data = dengue_flu, year, searches_dengue, continent, "Dengue fever occurrences for each continent")

```

## save_rds_csv
The `save_rds_csv` function can be used to save a dataframe as .rds and .csv file. In the code chunk below the usage of the function is demonstrated. 
```{r function 4, warning=FALSE, message=FALSE}

save_rds_csv("data_dengue", "new_dengue_data")

```
